### 2016-06-09 untitled.tex
more proofreading fixes

To date, the real-time literature on self-suspensions has focused on two task models: the \emph{dynamic} self-suspension model, which we discuss first,  and the  (\emph{multi}-)\emph{segmented} suspension model, which we discuss next in Section~\ref{sec:segmented}.  Self-suspensions can arise in both periodic and sporadic tasks (i.e, both interpretations of the $T_i$ parameter are possible). The observations that we make in this note apply equally to both periodic and sporadic tasks; for convenience, we focus primarily on periodic tasks.

@@

The root cause is increased interference due to the ``back-to-back'' execution effect~\cite{LSS:87,LSST:91,Ra:90,ABRTW:93,SLS:95}. In the example shown in Figure \ref{fig:not-ok-without-period-enforcement}, two jobs of $\tau_2$ execute in close succession (i.e, separated by less than a period) because the second job, released at time~10, self-suspended for a (much) shorter duration than the first job.  Consequently,  $\tau_3$ suffers from increased interference when $\tau_2$'s second job resumes ``too soon'' at time~12 after having been suspended for only one time unit, rather than four time units like the first job of $\tau_2$.

>>>>

To date, the real-time literature on self-suspensions has focused on two task models: the \emph{dynamic} self-suspension model, which we discuss first,  and the  (\emph{multi}-)\emph{segmented} suspension model, which we discuss next in Section~\ref{sec:segmented}.  Self-suspensions can arise in both periodic and sporadic tasks (i.e., both interpretations of the $T_i$ parameter are possible). The observations that we make in this note apply equally to both periodic and sporadic tasks; for convenience, we focus primarily on periodic tasks.

@@

The root cause is increased interference due to the ``back-to-back'' execution effect~\cite{LSS:87,LSST:91,Ra:90,ABRTW:93,SLS:95}. In the example shown in Figure \ref{fig:not-ok-without-period-enforcement}, two jobs of $\tau_2$ execute in close succession (i.e., separated by less than a period) because the second job, released at time~10, self-suspended for a (much) shorter duration than the first job.  Consequently,  $\tau_3$ suffers from increased interference when $\tau_2$'s second job resumes ``too soon'' at time~12 after having been suspended for only one time unit, rather than four time units like the first job of $\tau_2$.
